MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-08-31 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services. The community can recognize if those web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in the quality metric or throughput, the community can consider the new values as benchmark for future performance calculations, and penalize the suspicious web services. In this way, players will have incentive to truthfully reveal their real capabilities in order to profit best from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may degrade or improve, a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to be able to estimate their gain over time. However with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility base on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partit
ion of web services into communities, would make any brute-force type algorithm for best community selection strategy intractable and non-practical in real-world application settings.

@@

\subsection{Learning Date}\label{ss:learningdata}

\subsubsection{web services}\label{sss:webservices}
\subsubsection{filtered data}\label{sss:filtereddata}
\subsubsection{feature engineering}\label{sss:feng}
\subsubsection{feature vector generation}\label{sss:fvg}

>>>>

While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services. The community can recognize if those web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in the quality metric or throughput, the community can consider the new values as benchmark for future performance calculations, and penalize the suspicious web services. In this way, players will have incentive to truthfully reveal their real capabilities in order to profit best from the community and t  avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may degrade or improve, a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to be able to estimate their gain over time. However with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility base on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partition of web services into communities, would make any brute-force type algorithm for best community selection strategy intractable and non-practical in real-world application settings.

@@

In this section we describe our training process and methodology assisting services with a decision making mechanisms. We first present the training process and then we evaluate the learning model of web service in community settings.

\subsection{Learning Data}\label{ss:learningdata}

We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.

\subsubsection{web services}\label{sss:webservices}

We used a data set that is extracted from running web services. In this data set, each web service is associated with a number of features that reflect its functionality. To engage in communities, we add additional features that reflect web service’s utility as a result of joining other web services to form a community. The additional features are computed based on two assumptions that we adopt for community to be formed. Since we have 64 time slots of extracted features for each web service, we could build synthetic data set that contains features of large number of web services in a sequence of time. Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for testing web services. We have not implemented a learning model yet, but we do have all training data as well as validation and testing. So we are able to develop a classification algorithm that effectively classify web services and propose appropriate communities that best fit to web service’s requirements.

\subsubsection{filtered data}\label{sss:filtereddata}

\subsubsection{feature engineering}\label{sss:feng}
\subsubsection{feature vector generation}\label{sss:fvg}
